Automated Formal Synthesis of Provably Safe Digital Controllers for Continuous Plants

### 2019-01-30 automatica/paper.tex
typo
+ comments

Beyond the main requirement on safety, it is practically relevant to consider the 
constraints $\phi_\mathit{input}$ on the input
signal $u_{k}$ and $\phi_\mathit{init}$ on the initial states $x_0$,
which we assume have given bounds:
$\phi_\mathit{input} = \{\forall k \geq 0.\bigwedge_{i=1}^{p} \underline{u} \leq u_{i} \leq \overline{u}\} $,
and $\phi_\mathit{init} = \{ \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}\}$. 
The former constraint expresses that control input, possibly shaped via state-feedback, 
might saturates in view of physical constraints.

@@

Notice that the physical plant model operates over real-valued signals, 
which means that our verification phase must also account for the numerical error, 
as well as quantization errors caused by representing the physical plant at finite 
precision $\mathcal{F}_{\langle I_p,F_p \rangle}$.

>>>>

Beyond the main requirement on safety, it is practically relevant to consider the 
constraints $\phi_\mathit{input}$ on the input
signal $u_{k}$ and $\phi_\mathit{init}$ on the initial states $x_0$,
which we assume have given bounds:
$\phi_\mathit{input} = \{\forall k \geq 0.\bigwedge_{i=1}^{p} \underline{u} \leq u_{i} \leq \overline{u}\} $,
and $\phi_\mathit{init} = \{ \bigwedge_{i=1}^{n} \underline{x_{i,0}} \leq x_{i,0} \leq \overline{x_{i,0}}\}$. 
The former constraint expresses that control input, possibly shaped via state-feedback, 
might saturate in view of physical constraints.

@@

Notice that the physical plant model operates over real-valued signals, 
which means that our verification phase \note{I'm not sure that it's clear at this point what the verification phase consists of} must also account for the numerical error, 
as well as quantization errors caused by representing the physical plant at finite 
precision $\mathcal{F}_{\langle I_p,F_p \rangle}$. \note{Also, isn't this paragraph redundant after sec 3.7?}
